\Title

### 2021-01-06 manuscript/manuscript.tex
Explain how scaling limits the range of damping
Specify that in practice we find it's constrained to some values.

\noindent where $\lambda$ is a \emph{dimensionless} damping parameter and
regularization is applied on the scaled coefficients $\mathbf{m}$ instead of
$\mathbf{c}$.

@@

To improve the convergence of the algorithm, \citet{friedman2002} suggests that
introducing randomness into the fitting process. We achieve this by randomizing
the order in which the $K$ windows are used in the gradient boosting algorithm.

>>>>

\noindent where $\lambda$ is a \emph{dimensionless} damping parameter and
regularization is applied on the scaled coefficients $\mathbf{m}$ instead of
$\mathbf{c}$.
In practice, we find that suitable $\lambda$ values fall between $10^{-8}$ and
$10^{-1}$, irrespective of the dataset, and that results are mostly sensitive
to order-of-magnitude changes in $\lambda$.

@@

To improve the convergence of the algorithm, \citet{friedman2002} suggests
introducing randomness into the fitting process. We achieve this by randomizing
the order in which the $K$ windows are used in the gradient boosting algorithm.
